Concurrent Programming with CXL

### 2020-05-17 book/paper.tex
Getting close to something I like

\begin{figure}
\begin{code}
\begin{verbatim}
==== Livelock ====
__main__ () [0,35-63]    64 {'flags': {2: False, 1: False}, 'count': 0,
                                'done': {2: False, 1: False}}
up       1  [1-13,21-24] 25 {'flags': {2: False, 1: True}, 'count': 0,
                                'done': {2: False, 1: False}}
\end{verbatim}
\end{code}
\caption{Error output of Figure~\ref{fig:upflags}.}
\label{fig:upflagsoutput}
\end{figure}

@@

Figure~\ref{fig:upflags} presents a solution based on each process having
a flag indicating that it is trying to enter the critical section.
After setting the flag, the process waits until the other process is not
trying to enter the critical section.
If we run this program, the assertion does not fail.  In fact, this
solution does prevent both processes being in the critical section at
the same time.
However, it has a different problem called livelock: if both try to
enter the critical section at the same time, they may end up waiting for
one another.

>>>>

\begin{figure}
\begin{code}
\verbatiminput{UpTurn.cxl}
\end{code}
\caption{Naive use of turn variable to solve mutual exclusion.}
\label{fig:upturn}
\end{figure}

@@

Figure~\ref{fig:upflags} presents a solution based on each process having
a flag indicating that it is trying to enter the critical section.
After setting the flag, the process waits until the other process
(\texttt{1 - self}) is not trying to enter the critical section.
If we run this program, the assertion does not fail.  In fact, this
solution does prevent both processes being in the critical section at
the same time.
However, it has a different problem called livelock: if both try to
enter the critical section at the same time, they may end up waiting for
one another.
